### 2012-09-28 doc/prelim/document/chapters/parallel_mc/parallel_mc.tex
research proposal updates

\section{Monte Carlo Synthetic-Acceleration}
\label{sec:mcsa}
Using the ideas of Halton, Evans and Mosher recently developed a Monte
Carlo solution that was not prohibited severely by the quality of the
initial guess for the system \citep{evans_monte_2009} and later
applied it more rigorously as a solution mechanism for the radiation
diffusion equation \citep{evans_monte_2012}, achieving identical
numerical results as convential Krylov solvers. Their approach was
instead to use residual Monte Carlo as a synthetic acceleration for a
stationary method. To derive this method, we begin by splitting the
operator in Eq~(\ref{eq:linear_problem})
\begin{equation}
  \ve{x} = (\ve{I} - \ve{A})\ve{x} + \ve{b}\:.
  \label{eq:linear_split}
\end{equation}
With this we can then define the stationary method
\textit{Richardson's iteration} as:
\begin{equation}
  \ve{x}^{k+1} = (\ve{I} - \ve{A})\ve{x}^k + \ve{b}\:,
  \label{eq:richardsons_iteration}
\end{equation}
which will converge if $\rho(\ve{I} - \ve{A}) < 1$. We then define the
solution error at the $k^{th}$ iterate relative to the true solution:
\begin{equation}
  \delta \ve{x}^k = \ve{x} - \ve{x}^k\:.
  \label{eq:mcsa_error}
\end{equation}
Subtracting Eq~(\ref{eq:richardsons_iteration}) from
Eq~(\ref{eq:linear_split}) we get:
\begin{equation}
  \delta \ve{x}^{k+1} = (\ve{I} - \ve{A})\delta \ve{x}^k\:.
  \label{eq:mcsa_setup_1}
\end{equation}
Subtracting from this $(\ve{I} - \ve{A})\delta \ve{x}^{k+1}$ yields:
\begin{equation}
  \begin{split}
    \ve{A}\delta \ve{x}^{k+1} &= (\ve{I} -
    \ve{A})(\ve{x}^{k+1}-\ve{x}^{k}) \\ &= \ve{r}^{k+1}\:.
    \label{eq:mcsa_setup_2}
  \end{split}
\end{equation}
Using this, we define the following scheme that will converge in one
iteration if $\ve{A}$ is inverted exactly.
\begin{subequations}
  \begin{gather}
    \ve{x}^{k+1} = (\ve{I} - \ve{A})\ve{x}^k + \ve{b}\:,\\
    \ve{A} \delta \ve{x}^{k+1} = \ve{r}^{k+1}\:,\\
    \ve{x} = \ve{x}^{k+1} + \delta \ve{x}^{k+1}\:.
  \end{gather}
  \label{eq:mcsa_setup_3}
\end{subequations}
However, $\ve{A}$ is only approximately inverted by our numerical
methods and therfore we instead pose an iterative scheme in which the
Monte Carlo solvers are used to invert the operator. The
\textit{Fixed-Point Monte Carlo Synthetic-Acceleration} (MCSA) method
is defined as:
\begin{subequations}
  \begin{gather}
    \ve{x}^{k+1/2} = (\ve{I} - \ve{A})\ve{x}^k + \ve{b}\:,\\
    \ve{r}^{k+1/2} = \ve{b} - \ve{A}\ve{x}^{k+1/2}\:,\\
    \ve{A}\delta\ve{x}^{k+1/2} = \ve{r}^{k+1/2}\:,\\
    \ve{x}^{k+1} = \ve{x}^{k+1/2} + \delta \ve{x}^{k+1/2}\:,
  \end{gather}
  \label{eq:mcsa}
\end{subequations}
where the adjoint Monte Carlo method is used to generate the solution
correction from the residual. Using Monte Carlo in this way achieves
the same effect as Halton's method, decoupling its convergence rate
from the overall convergence rate of the method. Here, the approximate
Monte Carlo solution is not driven to a particular convergence as it
merely supplies a correction for the initial guess generated by
Richardson's iteration. Rather, only a set number of histories are
required using the adjoint method to generate the correction.

>>>>

\section{Monte Carlo Synthetic-Acceleration}
\label{sec:mcsa}
Using the ideas of Halton, Evans and Mosher recently developed a Monte
Carlo solution that was not prohibited severely by the quality of the
initial guess for the system \citep{evans_monte_2009} and later
applied it more rigorously as a solution mechanism for the radiation
diffusion equation \citep{evans_monte_2012}, achieving identical
numerical results as and marginally better performance than
conventional Krylov solvers. Their approach was instead to use
residual Monte Carlo as a synthetic acceleration for a stationary
method. To derive this method, we begin by splitting the operator in
Eq~(\ref{eq:linear_problem})
\begin{equation}
  \ve{x} = (\ve{I} - \ve{A})\ve{x} + \ve{b}\:.
  \label{eq:linear_split}
\end{equation}
With this we can then define the stationary method
\textit{Richardson's iteration} as:
\begin{equation}
  \ve{x}^{k+1} = (\ve{I} - \ve{A})\ve{x}^k + \ve{b}\:,
  \label{eq:richardsons_iteration}
\end{equation}
which will converge if $\rho(\ve{I} - \ve{A}) < 1$. We then define the
solution error at the $k^{th}$ iterate relative to the true solution:
\begin{equation}
  \delta \ve{x}^k = \ve{x} - \ve{x}^k\:.
  \label{eq:mcsa_error}
\end{equation}
Subtracting Eq~(\ref{eq:richardsons_iteration}) from
Eq~(\ref{eq:linear_split}) we get:
\begin{equation}
  \delta \ve{x}^{k+1} = (\ve{I} - \ve{A})\delta \ve{x}^k\:.
  \label{eq:mcsa_setup_1}
\end{equation}
Subtracting from this $(\ve{I} - \ve{A})\delta \ve{x}^{k+1}$ yields:
\begin{equation}
  \begin{split}
    \ve{A}\delta \ve{x}^{k+1} &= (\ve{I} -
    \ve{A})(\ve{x}^{k+1}-\ve{x}^{k}) \\ &= \ve{r}^{k+1}\:.
    \label{eq:mcsa_setup_2}
  \end{split}
\end{equation}
Using this, we define the following scheme that will converge in one
iteration if $\ve{A}$ is inverted exactly.
\begin{subequations}
  \begin{gather}
    \ve{x}^{k+1} = (\ve{I} - \ve{A})\ve{x}^k + \ve{b}\:,\\
    \ve{A} \delta \ve{x}^{k+1} = \ve{r}^{k+1}\:,\\
    \ve{x} = \ve{x}^{k+1} + \delta \ve{x}^{k+1}\:.
  \end{gather}
  \label{eq:mcsa_setup_3}
\end{subequations}
However, $\ve{A}$ is only approximately inverted by our numerical
methods and therfore we instead pose an iterative scheme in which the
Monte Carlo solvers are used to invert the operator. The
\textit{Fixed-Point Monte Carlo Synthetic-Acceleration} (MCSA) method
is defined as:
\begin{subequations}
  \begin{gather}
    \ve{x}^{k+1/2} = (\ve{I} - \ve{A})\ve{x}^k + \ve{b}\:,\\
    \ve{r}^{k+1/2} = \ve{b} - \ve{A}\ve{x}^{k+1/2}\:,\\
    \ve{A}\delta\ve{x}^{k+1/2} = \ve{r}^{k+1/2}\:,\\
    \ve{x}^{k+1} = \ve{x}^{k+1/2} + \delta \ve{x}^{k+1/2}\:,
  \end{gather}
  \label{eq:mcsa}
\end{subequations}
where the adjoint Monte Carlo method is used to generate the solution
correction from the residual. Using Monte Carlo in this way achieves
the same effect as Halton's method, decoupling its convergence rate
from the overall convergence rate of the method. Here, the approximate
Monte Carlo solution is not driven to a particular convergence as it
merely supplies a correction for the initial guess generated by
Richardson's iteration. Rather, only a set number of histories are
required using the adjoint method to generate the correction.

### 2012-09-28 doc/prelim/document/chapters/research_proposal/research_proposal.tex
research proposal updates

\chapter{Research Proposal}
\label{ch:research_proposal}
To develop the parallel MCSA and FANM methods, a research plan is
proposed to drive their development and quantify their merits and
feasiblity as compared to more conventional methods for linear and
nonlinear problems. We seek to rigorously verify both of these methods
and there implementation and will describe the means by which that
will be accomplished. Furthermore, the numerical experiments performed
will be constructed within a software framework that will permit an
agile development strategy. In this chapter we describe that
experimental framework and the progress achieved to date by its
use. In addition, we will a formulate a plan for verifying the new
stochastic methods and prepare a set of numerical experiments that
will determine some of their properties. Finally, we select a
challenge problem designed to potentially demsonstrate the
effectiveness of our new methods in the context of real-world,
production level applications.

@@

Generalizing MCSA for all linear problems has been achieved with both
the direct and adjoint Neumann-Ulam methods as the Monte Carlo solver
by leveraging the Epetra library within Trilinos
\citep{heroux_overview_2005}. Using Epetra (and its variants) we have
access to several features that will enhance future development and
experimentation. First, Epetra employs a compressed storage format for
sparse matrices as outlined in \S~\ref{subsec:fanm_storage}. This will
permit efficient memory use and permit the savings we expect by
implementing the FANM method. Second, Epetra is fully parallelized in
that the parallel graph structures and decomposed storage formats are
utilized to domain decompose both the operator and vector in the
linear system. These data structures provide access to the required
parallel matrix-vector operations outlined in
\S~\ref{sec:parallel_krylov_methods}. In addition, the parallel Monte
Carlo methods we will implement for the Neumann-Ulam methods as
outlined in \S~\ref{sec:parallel_stochastic_methods} will be greatly
facilitated and perhaps even enabled by these data
structures. Finally, the Epetra framework and its variants are
commonplace in many production level physics codes and therefore such
an implementation will provide an easy path to incorporating an MCSA
or FANM solver into those codes for further experimentation and
analysis.

\subsection{Direct vs. Adjoint Analysis}
\label{subsec:mcsa_direct_vs_adjoint}
Preliminary work has been completed to characterize the behavior of
the direct and adjoint Monte Carlo solvers with the MCSA
method\footnote{The contents of this section have been taken directly
  from my contributions to \citep{evans_monte_2012}}. The aim of this
initial work was to determine which of the two Monte Carlo solvers
provided the best MCSA performance. The MCSA method defined in
Eq.~(\ref{eq:mcsa}) uses the adjoint method to estimate the error
instead of the direct method outlined in \S~\ref{sec:direct_mc}. To
demonstrate the effectiveness of the adjoint method over the direct
method within the context of MCSA, we choose the 2D time-dependent
Poisson equation as a simple model problem:
\begin{equation}
  \frac{\partial \ve{u}}{\partial t} = \nabla^2 \ve{u}\:.
  \label{eq:poisson_equation}
\end{equation}
For all comparisons, a single time step is computed with backwards
Euler time integration. The Laplacian is differenced on a square
Cartesian grid with a second-order five-point stencil,
\begin{equation}
  \nabla^2_5 = \frac{1}{\Delta^2}[u_{i-1,j} + u_{i+1,j} + u_{i,j-1} +
    u_{i,j+1} - 4 u_{i,j}]\:,
  \label{eq:five_point_stencil}
\end{equation}
and a fourth-order nine-point stencil,
\begin{multline}
  \nabla^2_9 = \frac{1}{6\Delta^2}[4 u_{i-1,j} + 4 u_{i+1,j} + 4
    u_{i,j-1} + 4 u_{i,j+1} + u_{i-1,j-1}\\ + u_{i-1,j+1} +
    u_{i+1,j-1} + u_{i+1,j+1} - 20 u_{i,j}]\:,
  \label{eq:nine_point_stencil}
\end{multline}
both assuming a grid size of $\Delta$ in both the $i$ and $j$
directions. For a single time step solution, we then have the
following sparse linear system to be solved with the MCSA method:
\begin{equation}
  \ve{A} \ve{u}^{n+1} = \ve{u}^n\:.
  \label{eq:poisson_eq_lin_sys}
\end{equation}
Both the stencils will be used to vary the size and density of the
sparse linear system in Eq.~(\ref{eq:poisson_eq_lin_sys}).

@@

\subsection{MCSA Application to Finite Element Problems}
\label{subsec:mcsa_finite_element}
The Epetra-based MCSA implementation has enabled the solution of
finite element problems leveraging the Panzer finite element assembly
engine, providing an initial basis for our experimental framework. To
demonstrate this, consider the 2-dimensional steady-state heat
equation:
\begin{equation}
  \boldsymbol{\nabla} \cdot k \boldsymbol{\nabla} T = Q\:,
  \label{eq:heat_equation}
\end{equation}
where $k$ is the thermal conductivity, $T$ is the temperature, and $Q$
is the thermal source. We can write the heat equation in weak form
using Eq~(\ref{eq:fe_weak_form}):
\begin{equation}
  \int_{\Omega} \boldsymbol{\nabla}^T \ve{v} k \boldsymbol{\nabla} T
  d\Omega - \int_{\Omega} \ve{v}Q d\Omega - \int_{\Gamma} \ve{v}
  \bar{q} d\Gamma - \int_{\Gamma} \ve{v} k \frac{\partial T}{\partial
    n} d\Gamma= 0\:,
  \label{eq:weak_heat_equation}
\end{equation}
where the boundary conditions have now been incorporated. We can
interpret the last two integral terms as the contributions from a
fixed boundary flux source and the flux through the domain
boundary. This weak formulation can then be directly implemented
within the finite element assembly engine along with the appropriate
boundary conditions and source terms. For this example, we choose a
square Cartesian grid with boundary conditions as shown in
Figure~\ref{fig:heat_eq_setup}.  
\begin{figure}[htpb!]
  \begin{center}
    \scalebox{1.5}{
      \input{chapters/research_proposal/heat_eq_setup.pdftex_t} }
  \end{center}
  \caption{\textbf{Problem setup for finite element solution to 2D
      heat equation.} \textit{Dirichlet conditions are set for the
      temperature on all 4 boundaries of the Cartesian grid with
      thermal conductivity set to 2.0. No thermal source was
      present.}}
  \label{fig:heat_eq_setup}
\end{figure}
A value of 2.0 is used for $k$ with no thermal source and second-order
basis functions are chosen for the finite element form. This problem
was solved using Panzer to assemble the finite element system and
Jacobi preconditioned MCSA as the linear solver with the adjoint
Neumann-Ulam method as the Monte Carlo solver. The results of this
calculation are presented in Figure~\ref{fig:heat_eq_solution}.
\begin{figure}[htpb!]
  \centering
  \includegraphics[width=5in,clip]{chapters/research_proposal/heat_eq_solution.png}
  \caption{\textbf{Finite element solution to the 2D steady-state heat
      equation using MCSA.} \textit{A $100 \times 100$ Cartesian grid
      was used with Jacobi preconditioning applied to the linear
      system.}}
  \label{fig:heat_eq_solution}
\end{figure}

\section{Stochastic Methods Verification}
\label{sec:method_verification}

\section{Numerical Experiments}
\label{sec:numerical_experiments}

@@

>>>>

\chapter{Research Proposal}
\label{ch:research_proposal}
To develop the parallel MCSA and FANM methods, a research plan is
proposed to drive their development and quantify their merits and
feasiblity as compared to more conventional methods for linear and
nonlinear problems. We seek to rigorously verify both of these methods
and there implementation and will describe the means by which that
will be accomplished. Furthermore, the numerical experiments performed
will be constructed within a software framework that will permit an
agile development strategy. In this chapter we describe that
experimental framework and the progress achieved to date by its
use. In addition, we will a formulate a plan for verifying the new
stochastic methods and prepare a set of numerical experiments that
will determine some of their properties. Finally, we select a
large-scale challenge problem designed to potentially demonstrate the
effectiveness of our new methods in the context of real-world,
production level applications.

@@

Generalizing MCSA for all linear problems has been achieved with both
the direct and adjoint Neumann-Ulam methods as the Monte Carlo solver
by leveraging the Epetra library within Trilinos
\citep{heroux_overview_2005}. Using Epetra (and its variants) we have
access to several features that will enhance future development and
experimentation. First, Epetra employs a compressed storage format for
sparse matrices as outlined in \S~\ref{subsec:fanm_storage}. This will
permit efficient memory use and allow for the savings we expect by
implementing the FANM method. Second, Epetra is fully parallelized in
that the parallel graph structures and decomposed storage formats are
utilized to domain decompose both the operator and vectors in the
linear system. These data structures provide access to the required
parallel matrix-vector operations outlined in
\S~\ref{sec:parallel_krylov_methods}. In addition, the parallel Monte
Carlo methods we will implement for the Neumann-Ulam methods as
outlined in \S~\ref{sec:parallel_stochastic_methods} will be greatly
facilitated and perhaps even enabled by these data
structures. Finally, the Epetra framework and its variants are
commonplace in many production level physics codes and therefore such
an implementation will provide an easy path to incorporating an MCSA
or FANM solver into those codes for further experimentation and
analysis.

\subsection{Direct vs. Adjoint Analysis}
\label{subsec:mcsa_direct_vs_adjoint}
Preliminary work has been completed to characterize the behavior of
the direct and adjoint Monte Carlo solvers with the MCSA
method.\footnote{The contents of this section have been taken directly
  from my contributions to \citep{evans_monte_2012}} The aim of this
initial work was to determine which of the two Monte Carlo solvers
provided the best MCSA performance. The MCSA method defined in
Eq.~(\ref{eq:mcsa}) uses the adjoint method to estimate the error
instead of the direct method outlined in \S~\ref{sec:direct_mc}. To
demonstrate the effectiveness of the adjoint method over the direct
method within the context of MCSA, we choose the 2-dimensional
time-dependent Poisson equation as a simple model problem:
\begin{equation}
  \frac{\partial \ve{u}}{\partial t} = \nabla^2 \ve{u}\:.
  \label{eq:poisson_equation}
\end{equation}
For all comparisons, a single time step is computed with backwards
Euler time integration. The Laplacian is differenced on a square
Cartesian grid with a second-order five-point stencil,
\begin{equation}
  \nabla^2_5 = \frac{1}{\Delta^2}[u_{i-1,j} + u_{i+1,j} + u_{i,j-1} +
    u_{i,j+1} - 4 u_{i,j}]\:,
  \label{eq:five_point_stencil}
\end{equation}
and a fourth-order nine-point stencil,
\begin{multline}
  \nabla^2_9 = \frac{1}{6\Delta^2}[4 u_{i-1,j} + 4 u_{i+1,j} + 4
    u_{i,j-1} + 4 u_{i,j+1} + u_{i-1,j-1}\\ + u_{i-1,j+1} +
    u_{i+1,j-1} + u_{i+1,j+1} - 20 u_{i,j}]\:,
  \label{eq:nine_point_stencil}
\end{multline}
both assuming a grid size of $\Delta$ in both the $i$ and $j$
directions. For a single time step solution, we then have the
following sparse linear system to be solved with the MCSA method:
\begin{equation}
  \ve{A} \ve{u}^{n+1} = \ve{u}^n\:.
  \label{eq:poisson_eq_lin_sys}
\end{equation}
Both the stencils will be used to vary the size and density of the
sparse linear system in Eq.~(\ref{eq:poisson_eq_lin_sys}).

@@

\subsection{MCSA Application to Finite Element Problems}
\label{subsec:mcsa_finite_element}
The Epetra-based MCSA implementation has enabled the solution of
finite element problems leveraging the Panzer finite element assembly
engine, providing an initial basis for our experimental framework. To
demonstrate this, consider the 2-dimensional steady-state heat
equation:
\begin{equation}
  \boldsymbol{\nabla} \cdot k \boldsymbol{\nabla} T = Q\:,
  \label{eq:heat_equation}
\end{equation}
where $k$ is the thermal conductivity, $T$ is the temperature, and $Q$
is the thermal source. We can write the heat equation in weak form
using Eq~(\ref{eq:fe_weak_form}):
\begin{equation}
  \int_{\Omega} \boldsymbol{\nabla}^T \ve{v} k \boldsymbol{\nabla} T
  d\Omega - \int_{\Omega} \ve{v}Q d\Omega - \int_{\Gamma} \ve{v}
  \bar{q} d\Gamma - \int_{\Gamma} \ve{v} k \frac{\partial T}{\partial
    n} d\Gamma= 0\:,
  \label{eq:weak_heat_equation}
\end{equation}
where the boundary conditions have now been incorporated. We can
interpret the last two integral terms as the contributions from a
fixed boundary flux source and the flux through the domain
boundary. This weak formulation can then be directly implemented
within the finite element assembly engine along with the appropriate
boundary conditions and source terms. For this example, we choose a
square Cartesian grid with boundary conditions as shown in
Figure~\ref{fig:heat_eq_setup}.  
\begin{figure}[htpb!]
  \begin{center}
    \scalebox{1.5}{
      \input{chapters/research_proposal/heat_eq_setup.pdftex_t} }
  \end{center}
  \caption{\textbf{Problem setup for finite element solution to 2D
      heat equation.} \textit{Dirichlet conditions are set for the
      temperature on all 4 boundaries of the Cartesian grid with
      thermal conductivity set to 2.0. No thermal source was
      present.}}
  \label{fig:heat_eq_setup}
\end{figure}
A value of 2.0 is used for $k$ with no thermal source and second-order
basis functions are chosen for the finite element form. This problem
was solved using Panzer to assemble the finite element system and
Jacobi preconditioned MCSA as the linear solver with the adjoint
Neumann-Ulam method as the Monte Carlo solver. The results of this
calculation are presented in Figure~\ref{fig:heat_eq_solution}.
\begin{figure}[htpb!]
  \centering
  \includegraphics[width=5in,clip]{chapters/research_proposal/heat_eq_solution.png}
  \caption{\textbf{Finite element solution to the 2D steady-state heat
      equation using MCSA.} \textit{A $100 \times 100$ Cartesian grid
      was used with Jacobi preconditioning applied to the linear
      system.}}
  \label{fig:heat_eq_solution}
\end{figure}
In the results, we see the characteristic parabolic solution profiles
of the heat equation corresponding corresponding to the correct
Dirichlet condition. Based on this work, a finite element formulation
generated by the Panzer framework can be readily solved with a general
MCSA implementation. In addition, the above problem can already be
solved in parallel with conventional Krylov methods. Therefore, once a
parallel MCSA implementation is complete, this framework can be used
to generate those experiments and immediately compare to Krylov
methods. In addition, extension to nonlinear model problems requires
only a few small additions to the framework, providing the remainder
of the toolset we need for our analysis.

\section{Stochastic Methods Verification}
\label{sec:method_verification}
As we perform our numerical experiments, the results from the new
tools that we are using must be verified against benchmark
results. These benchmark tests should allow use to verify that the new
stochastic solvers that we develop generate the expected numerical
results in parallel for linear and nonlinear problems that have a
known, well-documented solution. In addition, as we explore parallel
strategies for the Monte Carlo methods and introduce bias or
non-reproducable results into our solution estimators, these
verification problems will allow us to determine if that cost is
acceptable. To verify the linear solvers, we will choose the above
2-dimensional heat equation problem in Eq~(\ref{eq:heat_equation}) on
a rectilinear grid for which analytical solutions are available. As a
complement to comparison with the analytical solutions, we may also
check those results against production implementations of Krylov
solvers. For the nonlinear solvers, we employ a new set of equations
with readily available benchmark solutions.

\subsection{FANM Verification}
\label{subsec:fanm_verification}
To verify the FANM method for nonlinear problems, we choose benchmark
solutions for the 2-dimensional, steady, incompressible Navier-Stokes
equations on a recitilinear grid in much the same way as Shadid and
Pawlowski's work on Newton-Krylov methods for the solution of these
equations \citep{shadid_inexact_1997,pawlowski_globalization_2006}. We
define these equations as follows :
\begin{subequations}
  \begin{gather}
    \rho \ve{u} \cdot \nabla \ve{u} - \nabla \cdot \ve{T} - \rho
    \ve{g} = \ve{0}
    \label{eq:ns_momentum}\\
    \nabla \cdot \ve{u} = 0
    \label{eq:ns_continuity}\\
    \rho C_p \ve{u} \cdot \nabla T + \nabla \cdot \ve{q} = 0\:,
    \label{eq:ns_energy}
  \end{gather}
  \label{eq:navier_stokes}
\end{subequations}
where $\rho$ is the fluid density, $\ve{u}$ is the fluid velocity,
$\ve{g}$ gravity, $C_p$ the specific heat capacity at constant
pressure of the fluid and $T$ the temperature of the
fluid. Eq~(\ref{eq:ns_momentum}) provides momentum transport,
Eq~(\ref{eq:ns_continuity}) provides the mass balance, and
Eq~(\ref{eq:ns_energy}) provides energy transport. In addition, we
close the system with the following equations:
\begin{subequations}
  \begin{gather}
    \ve{T} = -P \ve{I} + \mu[\nabla \ve{u} + \nabla \ve{u}^T]
    \label{eq:ns_stress_tensor}\\
    \ve{q} = - k \nabla T\:,
    \label{eq:ns_heat_flux}
  \end{gather}
  \label{eq:ns_closure}
\end{subequations}
where $\ve{T}$ is the stress tensor, $P$ is the fluid pressure, $\mu$
is the dynamic viscosity of the fluid, $\ve{q}$ is the heat flux in
the fluid, and $k$ is the thermal conductivity of the fluid. We will
then apply these equations to the following three benchmark problems.

\subsubsection{Thermal Convection Cavity Problem}
\label{subsubsec:natural_convection_cavity}

\subsubsection{Lid Driven Cavity Problem}
\label{subsubsec:lid_driven_cavity}

\subsubsection{Backward-Facing Step Problem}
\label{subsubsec:backward_facing_step}

\section{Numerical Experiments}
\label{sec:numerical_experiments}
Using the verification problems for the linear and nonlinear solvers
as a testing environment, we propose a set of experiments that will be
used to characterize several qualities of these stochastic methods.

@@

\section{Conclusion}
\label{sec:conclusion}
